What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-11 lda-paper.tex
minor change
Figures in Order..
spell checked

Imagine that a development team have agreed upon a set of features to
implement for their next interation, but these features were not
finished by the end of the iteration. The developers insist they were
focussed on the features, yet their manager and is not sure what
happened. In a scenario like this, topic analysis can help tease out
the topics of development that the developers were focussed on. Topic
analysis could highlight the orthogonal issues that developers were
spending time on.  Topic analysis extracts groups of words which from
documents (commit log messages) which can be used to relate
documents. These extracted topics often correlate with actual
development topics that the developers discussed. By applying topic
analysis locally to an iteration, both the developers and managers
might be able to see what were the topics of development.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{transitiveclosure}
  \caption{Topic similarity demonstrated by clustering topics by the transitive closure (connectedness)
    of topic similarity. Nodes are topics and
    arcs imply similarity. Similarity could be a measure such as
    topics share 8 out of 10 top ten words.}
\label{fig:closure}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fixed-time-smear-plot-cropped}
  \caption{A zoomed in slice of compact-trend-view of topics per month of MaxDB 7.500. The topic text is visible in each topic box. Trends are plotted across time continuously.}
  \label{fig:zoomedsmear}
\end{figure}

@@

We tracked Firebird from August 2000 to January 2006. We found that with a
similarity of $7/10$ that Firebird had far more continuous and
recurring trends than PosgreSQL.  The first large trend was segmented
across time but explicitly references one author \texttt{carlosga05}
and words like \emph{added}, \emph{fixed} and \emph{updated}.

@@

We noticed that commits that mentioned \emph{PHP} occurred two thirds
less frequently than commits that mentioned \emph{Perl}, but
\emph{Perl}-related topics appeared in the global static topics for
MaxDB while \emph{PHP}-related topics did not.  Our local topic
analysis mentioned \emph{PHP} in 5 different topics, yet only
mentioned \emph{Perl} in 4 different windoed topics and 1 global
topic. Perhaps this is because there was a cluster of \emph{Perl}
mentions during one month while \emph{PHP} was mentions were more
spread out.

We noticed that Perforce and Changelist were in just about every
topic, so we added them to the stop words list. As a result, longer
trends were shortened and in some cases the total number of topics
found per month was less.  Evaluating different similarity thresholds
showed that by removing common words one reduces the general
similarity of topics. That said, the larger topics still clearly
apparent. Thus if more relevant stop words are added one should tune
the topic similarity parameters to handle these changes.

>>>>

Imagine that a development team have agreed upon a set of features to
implement for their next iteration, but these features were not
finished by the end of the iteration. The developers insist they were
focussed on the features, yet their manager and is not sure what
happened. In a scenario like this, topic analysis can help tease out
the topics of development that the developers were focussed on. Topic
analysis could highlight the orthogonal issues that developers were
spending time on.  Topic analysis extracts groups of words which from
documents (commit log messages) which can be used to relate
documents. These extracted topics often correlate with actual
development topics that the developers discussed. By applying topic
analysis locally to an iteration, both the developers and managers
might be able to see what were the topics of development.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{transitiveclosure}
  \caption{Topic similarity demonstrated by clustering topics by the transitive closure (connectedness)
    of topic similarity. Nodes are topics and
    arcs imply similarity. Similarity could be a measure such as
    topics share 8 out of 10 top ten words.}
\label{fig:closure}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{fixed-time-smear-plot-cropped}
  \caption{A zoomed in slice of compact-trend-view of topics per month of MaxDB 7.500. The topic text is visible in each topic box. Trends are plotted across time continuously.}
  \label{fig:zoomedsmear}
\end{figure}

@@

We tracked Firebird from August 2000 to January 2006. We found that with a
similarity of $7/10$ that Firebird had far more continuous and
recurring trends than PostgreSQL.  The first large trend was segmented
across time but explicitly references one author \texttt{carlosga05}
and words like \emph{added}, \emph{fixed} and \emph{updated}.

@@

We noticed that commits that mentioned \emph{PHP} occurred two thirds
less frequently than commits that mentioned \emph{Perl}, but
\emph{Perl}-related topics appeared in the global static topics for
MaxDB while \emph{PHP}-related topics did not.  Our local topic
analysis mentioned \emph{PHP} in 5 different topics, yet only
mentioned \emph{Perl} in 4 different windowed topics and 1 global
topic. Perhaps this is because there was a cluster of \emph{Perl}
mentions during one month while \emph{PHP} was mentions were more
spread out.

We noticed that \emph{Perforce} and \emph{Changelist} were in just
about every topic, so we added them to the stop words list. As a
result, longer trends were shortened and in some cases the total
number of topics found per month was less.  Evaluating different
similarity thresholds showed that by removing common words one reduces
the general similarity of topics. That said, the larger topics still
clearly apparent. Thus if more relevant stop words are added one
should tune the topic similarity parameters to handle these changes.
